---
output: github_document
bibliography: vignettes/References.bib
---

<!-- README.md is generated from README.Rmd. Please edit README.Rmd. -->

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/SEAPSUTWorkflow)](https://cran.r-project.org/package=SEAPSUTWorkflow)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R build status](https://github.com/MatthewHeun/SEAPSUTWorkflow/workflows/check-master-develop/badge.svg)](https://github.com/MatthewHeun/SEAPSUTWorkflow/actions)
[![Travis-CI Build Status](https://travis-ci.org/MatthewHeun/SEAPSUTWorkflow.svg?branch=master)](https://travis-ci.org/MatthewHeun/SEAPSUTWorkflow)
[![Codecov test coverage](https://codecov.io/gh/EnergyEconomyDecoupling/SEAPSUTWorkflow/branch/master/graph/badge.svg)](https://codecov.io/gh/EnergyEconomyDecoupling/SEAPSUTWorkflow?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5091720.svg)](https://doi.org/10.5281/zenodo.5091720)
<!-- badges: end -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# SEAPSUTWorkflow

The `R` package SEAPSUTWorkflow provides functions and [drake](https://github.com/ropensci/drake) workflows for 
Societal Exergy Analysis (SEA) using the Physical Supply Use Table (PSUT) framework.


## Installation

<!-- You can install the released version of SEAPSUTWorkflow from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("SEAPSUTWorkflow") -->
<!-- ``` -->

<!-- And the development version from [GitHub](https://github.com/) with: -->
You can install `SEAPSUTWorkflow` from github with:

``` r
# install.packages("devtools")
devtools::install_github("MatthewHeun/SEAPSUTWorkflow")
```


## Example

To create a `drake` workflow, do this:

```{r example}
library(SEAPSUTWorkflow)
get_plan(countries = c("GHA", "ZAF"),
         additional_exemplar_countries = "World",
         max_year = 1999,
         ceda_data_folder = "ceda_path",
         machine_data_path = "machine_path",
         iea_data_path = "iea_path",
         exemplar_table_path = "exemplar_path",
         fu_analysis_folder = "fu_folder",
         reports_source_folders = "reports_source_path",
         reports_dest_folder = "reports_dest_path"
         )
```

## History

The functions in this package were used in ...
<!-- [Heun et al. [-@Heun:2018]](https://doi.org/10.1016/j.apenergy.2018.05.109). -->


## More Information

Find more information, including vignettes and function documentation, at 
<https://MatthewHeun.github.io/SEAPSUTWorkflow/>.


## References

