---
title: "PFUWorkflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PFUWorkflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PFUWorkflow)
```

## Introduction

`PFUWorkflow` is an `R` package that provides functions to build
a database of primary-to-final-to-useful (PFU) energy conversion chain (ECC)
societal exergy analyses (SEA).
`PFUWorkflow` makes use of the [drake](https://books.ropensci.org/drake/) package.
`PFUWorkflow` creates `drake` workflows that ensure that "What gets done stays done,"
leading to analyses that are more reproducible and less prone to errors.


## Quick start

To get started, follow these steps:

1. Create a new `R` project in a new folder or repository.
2. Make an `R` directory inside the new folder.
3. Inside the `R` directory, 
   make a file called `plan.R` that calls `PFUWorkflow::get_plan()` like this:

```{r}
plan <- PFUWorkflow::get_plan(countries = c("GHA", "ZAF"), 
                              max_year = 2017,
                              iea_data_path = "<<IEA extended energy balance path>>", 
                              country_concordance_path = "<<Country concordance path>>",
                              phi_constants_path = "<<phi constants path>>", 
                              ceda_data_folder = "<<CEDA temperature data path>>",
                              machine_data_path = "<<Machine data path>>",
                              exemplar_table_path = "<<exemplar table path>>",
                              fu_analysis_folder = "<<FU analysis folder>>", 
                              reports_source_folders = "<<Reports source folders>>",
                              reports_dest_folder = "<<Reports output folder>>",
                              pipeline_caches_folder = "<<Pipeline caches folder>>",
                              pipeline_releases_folder = "<<Pipeline releases folder>>",
                              release = FALSE)
```

where

* `countries` is the list of countries to be analyzed,
* `max_year` is the latest year to be analyzed,
* `<<IEA extended energy balance path>>` is the path to a `.csv` file that contains
[IEA](https://www.iea.org) [extended energy balance data](http://data.iea.org),
* `<<phi constants path>>` is the path to an Excel file of constant values of phi (the exergy-to-energy ratio),
* `<<CEDA temperature data path>>` is the path to CEDA cru_cy temperature data downloaded through `CEDATools`,
* `<<Machine data path>>` is the path to the Machine data excel files containing Eta.fu, Phi.u, and other data.
* `<<exemplar table path>>` is the path to an exemplar table (see below),
* `<<FU analysis folder>>` is the path to a folder containing final-to-useful analyses, 
* `<<Reports source folders>>` is a vector of paths to folders containing report sources (usually `.Rmd` and `.Rnw` files), 
* `<<Reports output folder>>` is the path to a folder for completed reports, 
* `<<Pipeline caches folder>>` is the path to a folder in which the pipeline cache is stored as a .zip file, and 
* `<<Pipeline releases folder>>` is the path to a folder in which releases of pipeline objects are stored.

The `plan` object is a data frame that provides a list of "targets" 
and code that will generate the target,
in the order the targets will be completed.

```{r}
plan
```

4. To visualize all dependencies in the plan,

```{r}
drake::vis_drake_graph(plan)
```

5. To execute the plan, call ``drake::make(plan)` or `drake::r_make(plan)`.
   When `drake ` is installed, the `Addins` menu contains the item `Run a drake workflow,`
   which sources the `plan.R` file and calls `drake::r_make(plan)`.


## Targets

A list of targets can be found with `PFUWorkflow::target_names`.
The meanings of the targets can be obtained with `?PFUWorkflow::target_names`.


## Results

To query the results of executing the plan, say `drake::readd(<<target>>)`,
where `<<target>>` is unquoted.
Alternatively, 
`drake::readd("<<target>>", character_only = TRUE)` for 
a string `<<target>>`.

Targets are computed by country. 
Say `PFUWorkflow::readd_by_country("<<target>>", "<<country>>")`
to obtain the value of a target for a country or vector of countries.
Both `<<target>>` and `<<country>>` need to be strings (enclosed in `""`)
for `PFUWorkflow::readd_by_country()`.



```{r, include = FALSE}
unlink(".drake", recursive=TRUE)
```
