---
title: "SEAPSUTWorkflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEAPSUTWorkflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SEAPSUTWorkflow)
```

## Introduction

`SEAPSUTWorkflow` is an `R` package that provides functions to build
a database of primary-to-final-to-useful (PFU) energy conversion chain (ECC)
societal exergy analyses (SEA).
`SEAPSUTWorkflow` makes use of the [drake](https://books.ropensci.org/drake/) package.
`SEAPSUTWorkflow` creates `drake` workflows that ensure that "What gets done stays done,"
leading to analyses that are more reproducible and less prone to errors.


## Quick start

To get started, follow these steps:

1. Create a new `R` project in a new folder or repository.
2. Make an `R` directory inside the new folder.
3. Inside the `R` directory, 
   make a file called `plan.R` that calls `SEAPSUTWorkflow::get_plan()` like this:

```{r}
plan <- SEAPSUTWorkflow::get_plan(countries = c("GHA", "ZAF"), 
                                  max_year = 2017,
                                  iea_data_path = "<<IEA extended energy balance path>>", 
                                  exemplar_table_path = "<<exemplar table path>>", 
                                  fu_analysis_folder = "<<FU analysis folder>>")
```

where

* `countries` is the list of countries to be analyzed,
* `max_year` is the latest year to be analyzed,
* `<<IEA extended energy balance path>>` is the path to a `.csv` file that contains
[IEA](https://www.iea.org) [extended energy balance data](http://data.iea.org),
* `<<exemplar table path>>` is the path to an exemplar table (see below), and
* `<<FU analysis folder>>` is the path to a folder containing final-to-useful analyses.

The `plan` object is a data frame that provides a list of "targets" 
and code that will generate the target,
in the order the targets will be completed.

```{r}
plan
```

4. To visualize all dependencies in the plan,

```{r}
drake::vis_drake_graph(plan)
```

5. To execute the plan, call ``drake::make(plan)` or `drake::r_make(plan)`.
   When `drake ` is installed, the `Addins` menu contains the item `Run a drake workflow,`
   which sources the `plan.R` file and calls `drake::r_make(plan)`.


## Targets

A list of targets can be found with `SEAPSUTWorkflow::target_names`.
The meanings of the targets can be obtained with `?SEAPSUTWorkflow::target_names`.


## Results

To query the results of executing the plan, say `drake::readd(<<target>>)`,
where `<<target>>` is unquoted.
Alternatively, 
`drake::readd("<<target>>", character_only = TRUE)` for 
a string `<<target>>`.

Targets are computed by country. 
Say `SEAPSUTWorkflow::readd_by_country("<<target>>", "<<country>>")`
to obtain the value of a target for a country or vector of countries.
Both `<<target>>` and `<<country>>` need to be strings (enclosed in `""`)
for `SEAPSUTWorkflow::readd_by_country()`.

